**Operating model**

### 2023-03-02 Rmd/report mac.Rmd

---
output:
  word_document:
    reference_docx: ../report_template.dotx
mathjax: TRUE
---

@@

source("../R/dd.R")
source("../R/pm.R")
source("../R/get_dropbox.R")

@@

<!-- =============================================================================================================== -->
<!-- ## Mackerel report                                                                                              -->
<!-- =============================================================================================================== -->

@@

<!-- =============================================================================================================== -->
<!-- Section 1: introduction                                                                                         -->
<!-- =============================================================================================================== -->

@@

The purpose of this work is to support the project “Fmsy-project for six high profile fish stocks”. The project focuses on the current management approach for fish stocks based on single-species Fmsy Values where the only density-dependent process that is included is recruitment. The project includes three other density-dependent population dynamics: growth (weight at age), sexual maturity and natural mortality.

@@

All MSE's have been developed within the FLR framework (https://flr-project.org/) and all the code is stored on github (https://github.com/martinpastoors/ddmse).

All data and results are available on DropBox (https://www.dropbox.com/sh/k87x074xqw7sgae/AAAmF980iR2n24wTkqhOhnpfa?dl=0)

<!-- =============================================================================================================== -->
<!-- Section 2: conditioning and summaries of ICES assessment                                                        -->
<!-- =============================================================================================================== -->

@@

_`r fig_nums("cond_waa")`_

@@

_`r fig_nums("cond_mat")`_

@@

_`r fig_nums("cond_natmor")`_

@@

_`r fig_nums("cond_ddwaa")`_

@@

_`r fig_nums("cond_gammwaa")`_

@@

_`r tab_nums("cond_gammsummary")`_

@@

_`r fig_nums("cond_lmwaa")`_

@@

_`r tab_nums("cond_gammcoefficients")`_

@@

_`r fig_nums("cond_ddmat")`_

@@

_`r fig_nums("cond_matogive")` _

<!-- =============================================================================================================== -->
<!-- Section 3: Estimating Density Dependent effects based on equilibrium analyses                                   -->
<!-- =============================================================================================================== -->

@@

_`r fig_nums("sim_dd3")`_

@@

_`r fig_nums("sim_yield")`_

<!-- =============================================================================================================== -->
<!-- Section 4: Setting up the Operating Models (OM)                                                                 -->
<!-- =============================================================================================================== -->

@@

_`r fig_nums("om_assessments")`_

@@

_`r fig_nums("om_VPADDM")`_

@@

_`r fig_nums("om_VPADDMM")`_

@@

_`r fig_nums("om_VPADDMMM")`_

@@

_`r fig_nums("om_eqyield")`_

@@

<!-- =============================================================================================================== -->
<!-- Section 5: Running forward projections                                                                          -->
<!-- =============================================================================================================== -->

@@

_`r fig_nums("mse_determ1")`_

@@

_`r fig_nums("mse_determ2")`_

@@

_`r fig_nums("mse_sim1")`_

@@

_`r fig_nums("mse_eq2050")`_

@@

_`r fig_nums("mse_eq2050")`_

<!-- =============================================================================================================== -->
<!-- Section 6: Discussion and conclusions                                                                           -->
<!-- =============================================================================================================== -->

@@

<!-- =============================================================================================================== -->
<!-- Funding                                                                                                         -->
<!-- =============================================================================================================== -->

@@

<!-- =============================================================================================================== -->
<!-- References                                                                                                      -->
<!-- =============================================================================================================== -->

@@

<!-- =============================================================================================================== -->
<!-- Annex 1: OM conditioning                                                                           -->
<!-- =============================================================================================================== -->

@@

<!-- =============================================================================================================== -->
<!-- Annex 2: Density dependent processes                                                                           -->
<!-- =============================================================================================================== -->

>>>>

---
output:
  word_document:
    reference_docx: ../report_template.dotx
mathjax: TRUE
bibliography: refs.bib
---

@lorenzen2000allometry

@@

source("../R/dd.R")
source("../R/pm.R")
source("../R/get_dropbox.r")

@@

<!-- =============================================================================================================== -->

<!-- ## Mackerel report                                                                                              -->

<!-- =============================================================================================================== -->

@@

<!-- =============================================================================================================== -->

<!-- Section 1: introduction                                                                                         -->

<!-- =============================================================================================================== -->

@@

The purpose of this work is to support the project "Fmsy-project for six high profile fish stocks". The project focuses on the current management approach for fish stocks based on single-species Fmsy Values where the only density-dependent process that is included is recruitment. The project includes three other density-dependent population dynamics: growth (weight at age), sexual maturity and natural mortality.

@@

All MSE's have been developed within the FLR framework (<https://flr-project.org/>) and all the code is stored on github (<https://github.com/martinpastoors/ddmse>).

All data and results are available on DropBox (<https://www.dropbox.com/sh/k87x074xqw7sgae/AAAmF980iR2n24wTkqhOhnpfa?dl=0>)

<!-- =============================================================================================================== -->

<!-- Section 2: conditioning and summaries of ICES assessment                                                        -->

<!-- =============================================================================================================== -->

@@

*`r fig_nums("cond_waa")`*

@@

*`r fig_nums("cond_mat")`*

@@

*`r fig_nums("cond_natmor")`*

@@

*`r fig_nums("cond_ddwaa")`*

@@

*`r fig_nums("cond_gammwaa")`*

@@

*`r tab_nums("cond_gammsummary")`*

@@

*`r fig_nums("cond_lmwaa")`*

@@

*`r tab_nums("cond_gammcoefficients")`*

@@

*`r fig_nums("cond_ddmat")`*

@@

*`r fig_nums("cond_matogive")`*

<!-- =============================================================================================================== -->

<!-- Section 3: Estimating Density Dependent effects based on equilibrium analyses                                   -->

<!-- =============================================================================================================== -->

@@

*`r fig_nums("sim_dd3")`*

@@

*`r fig_nums("sim_yield")`*

<!-- =============================================================================================================== -->

<!-- Section 4: Setting up the Operating Models (OM)                                                                 -->

<!-- =============================================================================================================== -->

@@

*`r fig_nums("om_assessments")`*

@@

*`r fig_nums("om_VPADDM")`*

@@

*`r fig_nums("om_VPADDMM")`*

@@

*`r fig_nums("om_VPADDMMM")`*

@@

*`r fig_nums("om_eqyield")`*

@@

<!-- =============================================================================================================== -->

<!-- Section 5: Running forward projections                                                                          -->

<!-- =============================================================================================================== -->

@@

*`r fig_nums("mse_determ1")`*

@@

*`r fig_nums("mse_determ2")`*

@@

*`r fig_nums("mse_sim1")`*

@@

*`r fig_nums("mse_eq2050")`*

@@

*`r fig_nums("mse_eq2050")`*

<!-- =============================================================================================================== -->

<!-- Section 6: Discussion and conclusions                                                                           -->

<!-- =============================================================================================================== -->

@@

<!-- =============================================================================================================== -->

<!-- Funding                                                                                                         -->

<!-- =============================================================================================================== -->

@@

<!-- =============================================================================================================== -->

<!-- References                                                                                                      -->

<!-- =============================================================================================================== -->

@@

<!-- =============================================================================================================== -->

<!-- Annex 1: OM conditioning                                                                           -->

<!-- =============================================================================================================== -->

@@

<!-- =============================================================================================================== -->

<!-- Annex 2: Density dependent processes                                                                           -->

<!-- =============================================================================================================== -->
